%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks, colorlinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\hypersetup{%
  colorlinks=true,% hyperlinks will be coloured
  linkcolor=blue,% hyperlink text will be green
  linkbordercolor=blue,% hyperlink border will be red
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Rishika Paul} \\ \vspace{1pt}
    \href{mailto:rishikapaul335@gmail.com}{\underline{rishikapaul335@gmail.com}} $|$ 
    \href{https://linkedin.com/in/rishika-paul}{\underline{LinkedIn Rishika Paul}} $|$
    \href{https://github.com/Rishika-335}{\underline{Github @Rishika-335}}
    
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.cuchd.in/}{Chandigarh University} [QS World University Ranking \textbf{231}]}{Mohali, Punjab}
      {B.E Computer Science and Engineering, \textbf{CGPA:} 8.4/10.0}{August 2023 -- Expected June. 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.hackbyte.in/}{HackByte 3.0}}{Madhya Pradesh}
      {Implementation}{April 2025}
      \resumeItemListStart
        \resumeItem{Awarded Best Beginner Team out of 128+ teams for building a smart musical glove using gesture-based input and multi-instrument sound playback.}
        \resumeItem{Designed and implemented the PyQt5-based desktop UI with real-time sensor data display and audio feedback.}
        \resumeItem{Developed backend logic in Python to process IMU, flex, and ToF sensor inputs, enabling accurate chord recognition across guitar, piano, and drum datasets.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://github.com/dev-sec-it/MediSwift-Partner}{MediSwift Partner- Medicine Delivery App}}{DEV SEC IT, Raiganj}
      {Android Developer Summer Intern}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built an Android app for delivery personnel using \textbf{Firebase Realtime Database}, \textbf{Authentication}, and \textbf{Cloud Messaging} for secure and real-time operations.}
        \resumeItem{Implemented scalable and modular codebase using \textbf{Jetpack Compose} and MVVM architecture.}
        \resumeItem{Integrated push notifications and dynamic order tracking tailored for real-world delivery operations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    
     \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://devfolio.co/projects/harmoni-hand-ca5e}{Harmoni Hand }}{[Arduino, Python, Sensors (IMU, Flex, ToF)]}}{April 2025}
          \resumeItemListStart
            \resumeItem{\textbf{Problem:} Traditional music learning requires different instruments, physical dexterity, and costly hardware—limiting access for beginners and differently-abled users. }
            \resumeItem{\textbf{Solution:}A smart glove-based musical interface that maps hand gestures and movements to chords in real-time, enabling audio playback for guitar, piano, and drums.}
            \resumeItem{\textbf{Designed With:} Cross-instrument gesture recognition—learn a gesture once and apply it across instruments for real-time feedback and sound. Increases accessibility by replacing complex instruments with a low-cost, portable glove that enables intuitive, gesture-based learning for all skill levels.}
            
          \resumeItemListEnd
    \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/Rishika-335/MedShare.git}{\textbf{MedShare}}}{ [ Kotlin, Java (Spring Boot), MongoDB, AWS]}}{January 2025 - April 2025}
          \resumeItemListStart
            \resumeItem{\textbf{Problem:} Limited access to essential medicines during late hours or emergencies in hostels and apartments. }
            \resumeItem{\textbf{Solution:} A real-time, peer-to-peer mobile app that allows users to request and share medicines nearby using location-based matching and instant communication. }
            \resumeItem{\textbf{Designed With: }Privacy-focused architecture and a clean, responsive user interface for quick emergency handling. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages(Proficient)}{: Java, Python, MySQL} \\
     \textbf{Frameworks(Proficient)}{: Jetpack Compose, Flask } \\
     \textbf{Languages(Familiar)}{: C, C++, Kotlin, Latex }\\
     \textbf{Other Skills}{: Microsoft tools (Powerpoint, Word, Excel), Figma, Canva }
    }}
 \end{itemize}
%-----------Professional Soft SKILLS-----------
\section{Interpersonal Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{Analytical \textbar{} Collaborative \textbar{} Adaptable \textbar{} Accountable \textbar{} Meticulous}
\end{itemize}


\section{Awards and Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \resumeItemListStart
                \resumeItem{\textbf{\href{https://www.linkedin.com/posts/rishika-paul_academicachiever2024-cuachievers-proudmoment-activity-7329553783133261824-rIKx?utm_source=share&utm_medium=member_desktop&rcm=ACoAAEUDyVEB38NT-gRomefAchmVkePi1lT5fGc}{Achiever's Award 2025 at Chandigarh University}}}
                \resumeItem{\textbf{\href{https://www.linkedin.com/posts/rishika-paul_hackbyte3-bestbeginnerteam-hackathon-activity-7316168620303085568-4Kkw?utm_source=share&utm_medium=member_desktop&rcm=ACoAAEUDyVEB38NT-gRomefAchmVkePi1lT5fGc}{Hackathon Winner at HackByte 3.0 }}
                \resumeItem{\textbf{Gold Medalist in International Mathematical Olympiad(IMO) in 2020}}
      \resumeItemListEnd
    }}
 \end{itemize}
 

\end{document}
